Git Learning Notes

### 2015-02-08 ch-wox/part1.tex
walked in to exchange opinions with Advr, and walking out with his on wox and moox
grammar overhaul, tense, clause, ISBN

\section{Introduction}
Tungsten oxides (\ce{WO_x}) is a group of important functional materials with distinctive properties and technology applications. Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields in the scientific community. Besides smart window based on \gls{ec} effect, tungsten oxides are also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, chemical and biological sensing based on gasochromic effect. In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.

In this chapter, a literature review on tungsten oxides and sodium tungsten oxides will be given first, with focus on technological applications, crystal structures, and synthesis approaches. Several growth methods were explored in this study to investigate the crystallographic dynamics of tungsten oxides and sodium tungsten oxides nanostructures. The characterization results were presented, followed by in-depth discussion. This chapter is concluded with a brief summary: the impurities effect on the formation of sodium tungsten oxides nanostructures and the seeded growth method for tungsten trioxide \glspl{nw} of high crystalline quality.

\subsection{Properties and Applications of Tungsten Oxides}\label{sec:wonawo}
Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases. The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its $+6$ oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant. A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}. These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise. 
% wo3 phases
\begin{table}[htb]
\centering
\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
\begin{tabular}{lccccc}
\toprule
&&&\multicolumn{3}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
\midrule
$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}
The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} And a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated. Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy. Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{octwo3.jpg}
\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
\label{fig:wo3oct}
\end{figure}

@@

Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states. The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ CS structure. Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row. Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} The enhancement arises from the structure composed of a conductive layer and an insulating layer that are laminated therein.\cite{Shingaya2013} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers. Localized surface plasmons could possibly exist on these conductive planes. Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}

@@

So far there is no unifying model that could reconcile these contradictory experimental observations. Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration. The concept of polaron was first proposed by Landau in 1933. In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling. A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away. The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.\cite{Devreese1996} In polaron model,\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions. This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron} the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}. During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when electron transition occurs from the hole polaron band to the electron polaron band.
\begin{align}\label{eq:ec}
x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$} \rightarrow \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$}
\end{align}
And the polaron binding energy ($E_p$) is given by
\begin{align}
E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1})
\end{align}
where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$. However, the polaron model has difficulty in estimating $r_p$. The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron in \ce{WO3}. Moreover, polaron model does not take oxygen vacancy into account, which plays a vital role in the nonstoichiometric tungsten oxides. For instance, it is observed that \ce{WO_{3-y}} films are metallic and conductive for $y > 0.5$, blue and conductive for $y = 0.3 \sim 0.5$, and transparent and resistive when $y < 0.3$, regardless of the preparation methods.\cite{Chatten2005}

Therefore another model in analogy to the F-color center is proposed. Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states. This defect level is expected to be inside or near the valence band. When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$. The positively charged vacancy exerts coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center. The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band) contributes to coloration.\cite{Deb2008}

So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration, but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model). A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice. Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}
\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
\end{align}
Similar scenario occurs in the gasochromic effect. Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases. Both consent to Eq.~\ref{eq:cl_bl1}. But there is a disagreement on the final states. Double injection supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules. Both have been substantiated experimentally. Therefore the exact mechanism in \ce{WO_x} still requires further investigation.

\subsection{Review of Synthesis Methods}\label{sec:woxgrowth}

As the chemical formula \ce{WO3} suggested, the most straightforward way is heating metallic tungsten in various forms,\cite{Zhou2005a,Cao2009,Hsieh2010} i.e., powders, foils and wires. Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species. Therefore scalable growth seems difficult at low temperature range unless other activation mechanisms are used. The DC current heating proved to be a route with potential large yield. Tungsten wire or filament is connected to a current source, and substrate is positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007} Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e. water, \ce{H2}, or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$ \si{\degreeCelsius}) than that of metallic tungsten.

In contrast, organometallic decomposition is another feasible method. \citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius}, and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005} Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique. Typical process flow is: the precursor solution is pumped to an atomizer, and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates. Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011} Main reactions include:
\begin{align}
\cee{W + O2 &\rightarrow WO_{3-x}\\
W + H2O &\rightarrow  W_{3-x} + H2}
\end{align}

Hydrothermal method has been an important route to synthesize a diversity of nanomaterials. Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom. Then the solution is transferred into a sealed container (i.e. Teflon autoclave) and maintained at elevated temperature ($120 \sim 300$ \si{\degreeCelsius}) for tens of hours. Finally the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products. A brief summary of representative synthesis methods is shown in Table~\ref{tab:wox}.

>>>>

\section{Introduction}
Tungsten oxides (\ce{WO_x}) is a group of important functional materials with distinctive properties and technology applications. Intense research interest was rekindled by the discovery of \gls{ec} effect in \citeyear{Granqvist1993}.\cite{Granqvist1993}  Nano-engineering \ce{WO_x} bring more possibility and flexibility to its already rich characteristics, therefore resulting in research efforts spanning multiple fields in the scientific community. Besides smart window based on \gls{ec} effect, tungsten oxides are also well investigated for several other significant applications: photoelectrochemical cell for solar energy conversion and storage, photocatalysis for hydrogen evolution reaction, and chemical and biological sensing based on gasochromic effect. In addition, a few young fields are not thoroughly explored: field emission, optical storage, thermo-electricity, ferro-electricity, and superconductivity.

In this chapter, a literature review on tungsten oxides and sodium tungsten oxides is introduced first, with focus on technological applications, crystal structures, and synthesis approaches. Several growth methods were explored in this study to investigate the crystallographic dynamics of tungsten oxides and sodium tungsten oxides nanostructures. The characterization results were presented, followed by in-depth discussion. This chapter is concluded with a brief summary: the impurities effect on the formation of sodium tungsten oxides nanostructures and the seeded growth method for tungsten trioxide \glspl{nw} of high crystalline quality.

\subsection{Properties and Applications of Tungsten Oxides}\label{sec:wonawo}
Tungsten trioxide (\ce{WO3}) crystallizes in multiple phases. The basic building block is \ce{WO6} octahedra.\footnote{Tungsten, with its electronic configuration as \ce{(Xe)4f^{14}5d^{4}6s^{2}}, has empty 5d and 6s orbitals in its $+6$ oxidation state.} \ce{WO3} crystal structure consists of \ce{WO6} octahedra joined at their corners, which may be considered as a perovskite structure of \ce{CaTiO3} with all \ce{Ca^{2+}} sites vacant. A representative lattice structure is illustrated in Fig.~\ref{fig:wo3oct}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{octwo3.jpg}
\caption[Octahedra model of \ce{WO3}]{Octahedra model of \ce{WO3}}
\label{fig:wo3oct}
\end{figure}
These distorted \ce{WO6} octahedra adapt different tilting angles in different phases and edge-sharing octahedra also arise. 
% wo3 phases
\begin{table}[htb]
\centering
\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
\begin{tabular}{lccccc}
\toprule
&&&\multicolumn{3}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
\midrule
$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}
The temperature-dependent phase transition and corresponding lattice constants in bulk form is summarized in Table~\ref{tab:wo3phase}.\cite{Zheng2011} \ce{WO3} in monoclinic phase is favored in room temperature; however, a firm assignation of space group to monoclinic phases are still in debate.\cite{Chatten2005} It is noticed that the lattice parameters obtained via \emph{ab initio} calculation closely match the experimental values.\cite{Migas2010a} The phase transition scenarios in nanostructured \ce{WO3} are supposed to be more sophisticated. Within Gibbs-Thomson framework, one can generally expect lower transition temperature than their bulk counterparts due to enhanced surface energy. Temperature-dependent Raman spectroscopy provided support for this deduction.\cite{Boulova2002}

@@

Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states. The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure. Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=W_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row. Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers. Localized surface plasmons could possibly exist on these conductive planes. Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}

@@

So far there is no unifying model that could reconcile these contradictory experimental observations. Among all the developed models, polaronic absorption is the most widely accepted mechanism for coloration. The concept of polaron was first proposed by Landau in 1933. In ionic or highly polar crystals, such as II-VI semiconductors, alkali halides, and transition metal oxides, the Coulomb interaction between a conduction electron and the lattice ions results in a strong electron-phonon coupling. A new quasi-particle, virtual phonon, can be defined corresponding to the effect of electron pulling nearby positive ions towards it and pushing nearby negative ions away. The electron and its virtual phonons, taken together, can be treated as a new composite particle, called an electron polaron; the hole polaron is defined analogously.\cite{Devreese1996} In polaron model,\footnote{When a free electron travels through a polar solid, it creates a local lattice displacement (longitudinal optical phonon clouds) due to the coulombic interaction with neighboring ions. This local distortion and the electron together is equivalent to a new elementary exciton of the crystal, and is named as polaron} the intercalation of \ce{M^+} (M = H, \ce{Li}, or Na) ions into \ce{WO3} films is accompanied with the formation of small polarons ($r_p$ comparable to unit cell size) and formal reduction of some \ce{W^{6+}} sites to \ce{W^{5+}}, as depicted in Eq.~\ref{eq:ec}. 
\begin{align}\label{eq:ec}
x\ce{M+} + x\ce{e-} +  \ce{$\alpha \hyphen$WO$_{3-y}$} \rightarrow \ce{$\alpha \hyphen$M$_x$WO$_{3-y}$}
\end{align}
During the intercalation process, the \ce{M^+} ions enter into these vacant sites.\cite{Hepel2008} Coloration occurs when electron transition occurs from the hole polaron band to the electron polaron band. And the polaron binding energy ($E_p$) is given by
\begin{align}
E_p = - \frac{e^2}{2r_p} (\epsilon_\infty^{-1} - \epsilon_{st}^{-1})
\end{align}
where $\epsilon_\infty$ and $\epsilon_{st}$ are optical and static dielectric constants, respectively, and polaron radius $r_p$, which specifies how far the lattice distortion extends, is related to polaron density $N_p$ by $r_p = \frac{1}{2}\sqrt[3]{\pi/6N_p}$. However, the polaron model has difficulty in estimating $r_p$. The asymmetric optical absorption spectrum are often characteristic of large polarons, and dielectric constants ($\epsilon_\infty = 6.52,\epsilon_{st} > 50$,\cite{Deb2008}) suggests the formation of bipolaron in \ce{WO3}. Moreover, polaron model does not take oxygen vacancy into account, which plays a vital role in the nonstoichiometric tungsten oxides. For instance, it is observed that \ce{WO_{3-y}} films are metallic and conductive for $y > 0.5$, blue and conductive for $y = 0.3 \sim 0.5$, and transparent and resistive when $y < 0.3$, regardless of the preparation methods.\cite{Chatten2005}

Therefore another model in analogy to the F-color center is proposed. Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states. This defect level is expected to be inside or near the valence band. When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$. The positively charged vacancy exerts Coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center. The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band) contributes to coloration.\cite{Deb2008}

So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration; but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model). A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice. Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}
\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
\end{align}
Similar scenario occurs in the gasochromic effect. Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases. Both consent to Eq.~\ref{eq:cl_bl1}. But there is a disagreement on the final states. Double injection model supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules. Both have been substantiated experimentally;\cite{Zhu2010} therefore, the exact mechanism in \ce{WO_x} still requires further investigation.

\subsection{Review of Synthesis Methods of Tungsten Oxides}\label{sec:woxgrowth}

As the chemical formula \ce{WO3} suggested, the most straightforward way is heating metallic tungsten (W) in various forms,\cite{Zhou2005a,Cao2009,Hsieh2010} i.e., powders, foils, and wires. Actually \ce{WO_x} \glspl{nw}\footnote{$x$ is between 2 and 3} were observed when directly heating W wires.\cite{Gu2002a} Due to the extreme high melting point of W, it requires very high temperature (say, above 1100 \si{\degreeCelsius}) to produce large amount of growth species. Therefore scalable growth seems difficult at low temperature range unless other activation mechanisms are used. The dc current heating proved to be a route with potential large yield, where tungsten wire or filament was connected to a current source, and substrate was positioned in proximity to the heated W wire.\cite{Lingfei2006,Thangala2007,Chang2007} Tungsten oxides powder can also been used as precursor to prepare \ce{WO_{x}} \glspl{nw}.\cite{Huang2008a,Wang2009} Hydrogen-containing agents (i.e. water, \ce{H2}, or methane\cite{Klinke2005}) were often involved into the reaction.\cite{Baek2007,Karuppanan2007} The potential benefit is \ce{WO3} has a much lower melting point ($\approx 1470$ \si{\degreeCelsius}) than that of metallic tungsten.

Meanwhile, organometallic decomposition is another feasible method. \citeauthor{Pol2005} obtained \ce{W18O49} nanorods by thermal dissociation of \ce{WO(OMe)4} at 700 \si{\degreeCelsius} and \ce{WO3} by further annealing at 500 \si{\degreeCelsius} in air atmosphere.\cite{Pol2005} Spray pyrolysis is a typical aerosol-assisted \gls{cvd} technique. Typical process flow is: the precursor solution is pumped to an atomizer and then sprayed through the carrier gas as a fine mist of very small droplets onto heated substrates. Subsequently the droplets undergo evaporation, solute condensation, and thermal decomposition, which then result in film formation.\cite{Zheng2011} Main reactions include:
\begin{align}
\cee{W + O2 &\rightarrow WO_{3-x}\\
W + H2O &\rightarrow  W_{3-x} + H2}
\end{align}

Besides, hydrothermal method has been an important route to synthesize a diversity of nanomaterials. Preparation of \ce{WO_{3-x}} has also been demonstrated hydrothermally.\cite{Lee2003,Gu2007} Usually, the precursor (\ce{H2WO4}) is mixed with other reactants (sulfides or certain organic acid) in solution and pH value is adjusted as another control degree of freedom. Then, the solution is transferred into a sealed container (i.e. Teflon autoclave) and maintained at elevated temperature ($120 \sim 300$ \si{\degreeCelsius}) for tens of hours. Finally, the product is separated from the solution and dried, layered \ce{WO3.nH2O} flakes are usual products. A brief summary of representative synthesis methods is shown in Table~\ref{tab:wox}.
